Рекомендации по подготовке статей к публикации

### 2023-03-02 paper/jmlda/jmlda-template-rus.tex
initial commit
initial commit

\documentclass[12pt, twoside]{article}
\usepackage{jmlda}
\usepackage[utf8]{inputenc}
\usepackage[english,main=russian]{babel}
\usepackage[T2A]{fontenc}
\newcommand{\hdir}{.}

\begin{document}
\English

\title
	[JMLDA paper template] % short title for page headings, not necessary if a full title fits the headings
    {Machine Learning and Data Analysis journal paper template} % full title
\author
	[F.\,S.~Author] % short list of the authors (<= 3) for page headings, is necessary only if the full list does not fit the headings
	{F.\,S.~Author, F.\,S.~Co-Author, and F.\,S.~Name} % full list of the authors, presented in the table of contetns of the issue
    [F.\,S.~Author$^1$, F.\,S.~Co-Author$^2$, and F.\,S.~Name$^{1, 2}$] % list of the authors presented in the title page of the article, is necessary only if it differs from the full list of the authors in braces, i.e. '{' and '}'
\email
    {author@site.ru; co-author@site.ru; co-author@site.ru}
\thanks
    {The research was
     %partially
     supported by the Russian Foundation for Basic Research (grants 00-00-0000 and 00-00-00001).}
\organization
    {$^1$Organization, address;
     $^2$Organization, address}
\abstract
    {This is the template of the paper submitted to the journal ``Machine Learning and Data Analysis''.

@@

\titleRus
    [Шаблон статьи для публикации] % short title for page headings, not necessary if a full title fits the headings
    {Шаблон статьи для публикации в журнале <<Машинное обучение и анализ данных>>} % full title
\authorRus
    [И.\,О.~Автор] % short list of the authors (<= 3) for page headings, is necessary only if the full list does not fit the headings
    {И.\,О.~Автор, И.\,О.~Соавтор, И.\,О.~Фамилия} % full list of the authors, presented in the table of contetns of the issue
    [И.\,О.~Автор$^1$, И.\,О.~Соавтор$^2$, И.\,О.~Фамилия$^{1,2}$] % list of the authors presented in the title page of the article, is necessary only if it differs from the full list of the authors in braces, i.e. '{' and '}'
\thanksRus
    {Работа выполнена при
     %частичной
     финансовой поддержке РФФИ, проекты \No\ \No 00-00-00000 и 00-00-00001.}
\organizationRus
    {$^1$Организация, адрес; $^2$Организация, адрес}
\abstractRus
    {Данный текст является шаблоном статьи, подаваемой для публикации в журнале <<Машинное обучение и анализ данных>>.

%these fields are filled in by the journal editors
\doi{10.21469/22233792}
\receivedRus{01.01.2017}
\receivedEng{January 01, 2017}

@@

\section{Introduction}
\noindent %this command is placed at the beginning of the first sentence of each paragraph/section only.
In this section state the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results.

\section{Preparing a manuscript}
\noindent
Manuscripts are prepared using \verb'jmlda.sty' style package.
You are recommended to use \verb'jmlda_rus.bst' and \verb'jmlda_eng.bst' style files for generating bibliography using Bib\TeX.

Visit the \url{http://jmlda.org/?lang=en} website for detailed submission instructions, templates and other information.

Please note that this file must be saved in~\verb'UTF-8' encoding. Where possible select~\verb'UTF-8 without BOM' encoding. 
To change the encoding please use \verb'Sublime Text' or \verb'Notepad++' text editors.

\section{Structure of the article}
\noindent
Divide your article into clearly defined and numbered sections and paragraphs.

\paragraph{Paragraph}
\noindent
Sections and paragraphs are numbered and have a brief heading.

%please do not change the name of this section if it is present
\section{Concluding Remarks}
This section should provide the summary and explore the significance of the results achieved and list problems not yet solved.
Results should be clear and concise.

%%%% please specify doi of the cited item if possible, see~\bibitem{article}
%%%% Crossref doi of the item can be retrieved at http://www.crossref.org/guestquery/
\begin{thebibliography}{99}

\bibitem{book}
	\BibAuthor{Goossens,~M., F. Mittelbach, and A.~Samarin}. 1994.
	\BibTitle{The \LaTeX\ companion}.
	2nd ed.
	Reading, MA: Addison-Wesley. 528 p.

@@

\maketitleSecondary
\Russian
%%%% please specify doi of the cited item if possible, see~\bibitem{article}
%%%% Crossref doi of the item can be retrieved at http://www.crossref.org/guestquery/
\begin{thebibliography}{99}
\bibitem{book}
    \BibAuthor{Гуссенс~М., Миттельбах~Ф., Cамарин~А.}
    \BibTitle{Путеводитель по пакету \LaTeX\ и~его расширению \LaTeXe} / Пер. с англ.~---
    М.:~Мир, 1999. 606~с.
    (\BibAuthor{Goossens M., Mittelbach F., Samarin A.}
     \BibTitle{The \LaTeX\ companion}.~--- 2nd ed.~--- Reading, MA, USA: Addison-Wesley, 1994. 528 p.)

>>>>

\documentclass[12pt, twoside]{article}
\usepackage{jmlda}
\newcommand{\hdir}{.}

\begin{document}

\title
    [Шаблон статьи для публикации] % краткое название; не нужно, если полное название влезает в~колонтитул
    {Шаблон статьи для публикации в журнале <<Машинное обучение и анализ данных>>}
\author
    [И.\,О.~Автор] % список авторов (не более трех) для колонтитула; не нужен, если основной список влезает в колонтитул
    {И.\,О.~Автор, И.\,О.~Соавтор, И.\,О.~Фамилия} % основной список авторов, выводимый в оглавление
    [И.\,О.~Автор$^1$, И.\,О.~Соавтор$^2$, И.\,О.~Фамилия$^{1,2}$] % список авторов, выводимый в заголовок; не нужен, если он не отличается от основного
\email
    {author@site.ru; co-author@site.ru;  co-author@site.ru}
\thanks
    {Работа выполнена при
     %частичной
     финансовой поддержке РФФИ, проекты \No\ \No 00-00-00000 и 00-00-00001.}
\organization
    {$^1$Организация, адрес; $^2$Организация, адрес}
\abstract
    {Данный текст является шаблоном статьи, подаваемой для публикации в журнале <<Машинное обучение и анализ данных>>.

\titleEng
	[JMLDA paper template] % краткое название; не нужно, если полное название влезает в~колонтитул
    {Machine Learning and Data Analysis journal paper template}
\authorEng
	[F.\,S.~Author] % список авторов (не более трех) для колонтитула; не нужен, если основной список влезает в колонтитул
	{F.\,S.~Author, F.\,S.~Co-Author, and F.\,S.~Name} % основной список авторов, выводимый в оглавление
    [F.\,S.~Author$^1$, F.\,S.~Co-Author$^2$, and F.\,S.~Name$^{1, 2}$] % список авторов, выводимый в заголовок; не нужен, если он не отличается от основного
\thanksEng
    {The research was
     %partially
    	 supported by the Russian Foundation for Basic Research (grants 00-00-0000 and 00-00-00001).
    }
\organizationEng
    {$^1$Organization, address; $^2$Organization, address}
\abstractEng
    {This is the template of the paper submitted to the journal ``Machine Learning and Data Analysis''.

@@

%данные поля заполняются редакцией журнала
\doi{10.21469/22233792}
\receivedRus{01.01.2017}
\receivedEng{January 01, 2017}

@@

\section{Введение}
После аннотации, но перед первым разделом,
располагается введение, включающее в себя
описание предметной области,
обоснование актуальности задачи,
краткий обзор известных результатов.

\section{Название раздела}
Данный документ демонстрирует оформление статьи,
подаваемой в электронную систему подачи статей \url{http://jmlda.org/papers} для публикации в журнале <<Машинное обучение и анализ данных>>.
Более подробные инструкции по~стилевому файлу \texttt{jmlda.sty} и~использованию издательской системы \LaTeXe\
находятся в~документе \texttt{authors-guide.pdf}.
Работу над статьёй удобно начинать с~правки \TeX-файла данного документа.

Обращаем внимание, что данный документ должен быть сохранен в кодировке~\verb'UTF-8 without BOM'.
Для смены кодировки рекомендуется пользоваться текстовыми редакторами \verb'Sublime Text' или \verb'Notepad++'.

\paragraph{Название параграфа}
Разделы и~параграфы, за исключением списков литературы, нумеруются.

\section{Заключение}
Желательно, чтобы этот раздел был, причём он не~должен дословно повторять аннотацию.
Обычно здесь отмечают, каких результатов удалось добиться, какие проблемы остались открытыми.

%%%% если имеется doi цитируемого источника, необходимо его указать, см. пример в \bibitem{article}
%%%% DOI публикации, зарегистрированной в системе Crossref, можно получить по адресу http://www.crossref.org/guestquery/
\begin{thebibliography}{99}
\bibitem{book}
    \BibAuthor{Гуссенс~М., Миттельбах~Ф., Cамарин~А.}
    \BibTitle{Путеводитель по пакету \LaTeX\ и~его расширению \LaTeXe} / Пер. с англ.~---
    М.:~Мир, 1999. 606~с.
    (\BibAuthor{Goossens M., Mittelbach F., Samarin A.}
     \BibTitle{The \LaTeX\ companion}.~--- 2nd ed.~--- Reading, MA, USA: Addison-Wesley, 1994. 528 p.)

%%%% если имеется doi цитируемого источника, необходимо его указать, см. пример в \bibitem{article}
%%%% DOI публикации, зарегистрированной в системе Crossref, можно получить по адресу http://www.crossref.org/guestquery/.

\maketitleSecondary
\English
\begin{thebibliography}{99}
\bibitem{book}
	\BibAuthor{Goossens,~M., F. Mittelbach, and A.~Samarin}. 1994.
	\BibTitle{The \LaTeX\ companion}.
	2nd ed.
	Reading, MA: Addison-Wesley. 528 p.

@@
